Online Verification of Commutativity

### 2020-08-02 acmPaper/paper.tex
half a sentence

\section{Evaluation}
We compare performance of the following path checking algorithms: (1) naive baseline (2) less naive, two-flip baseline (3) batch baseline (4) algorithm ~\ref{algo_online_polynomial}, and (5) algorithm ~\ref{algo_online_minimal}.
The two aspects we look at are time for response and size of response set (smaller sets -- tighter output results -- would mean less calls to the oracle).
We use randomly generated graphs for benchmarking, and vary their size.
Given a graph and a new edge, we time how long it takes for an algorithm to return 
All computation was performed on a Macbook Pro 2015, 2.9 GHz Dual-Core Intel Core i5.

>>>>

\section{Evaluation}
We compare performance of the following path checking algorithms: (1) naive baseline (2) less naive, two-flip baseline (3) batch baseline (4) algorithm ~\ref{algo_online_polynomial}, and (5) algorithm ~\ref{algo_online_minimal}.
The two aspects we look at are time for response and size of response set (smaller sets -- tighter output results -- would mean less calls to the oracle).
We use randomly generated graphs for benchmarking, and vary their size.
Given a graph and a new edge, we time how long it takes for an algorithm to return  the set of pairs that need to be verified.
All computation was performed on a Macbook Pro 2015, 2.9 GHz Dual-Core Intel Core i5.
